---
title: "Lab 9 A"
author: "Nathan Haywood"
date: "12/4/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("stringr")
library("tidyverse")
```

```{r}
x <- c("apple", "banana", "pear")
str_view(x, "an")
str_view(x, ".a.")
```

```{r}
dot <- "\\."
writeLines(dot)
```

```{r}
x <- c("abc", "a.c", "bef")
str_view(x, "a\\.c")
```

```{r}
x <- "a\\b"
writeLines(x)

str_view(x, "\\\\")
```

## Exercise 14.3.1.1
#### The first  wont match because \ is used to escape the following character. The second and third wont match because theyll resolve the prior \s and will escape the next character.  

```{r}
x <- c("apple", "banana", "pear")
str_view(x, "^a")
str_view(x, "a$")
```

```{r}
x <- c("apple pie", "apple", "apple cake")
str_view(x, "apple")
str_view(x, "^apple$")
```

## Exercise 14.3.2.1
```{r}
str_view(c("$^$", "ab$^$", "$^$cd"), "^\\$\\^\\$$")
```

```{r}
x <- c("abc", "a.c", "a*c", "a c")
str_view(x, "a[.]c")
str_view(x, ".[*]c")
str_view(x, "a[ ]")
```

```{r}
x <- c("grey", "gray")
str_view(x, "gr(e|a)y")
```

## Exercise 14.3.3.1
```{r}
str_view(x, "^[aeiou]")
str_view(x, "^[aeiou]", match = FALSE)
str_view(x, "[^e]ed$")
str_view(x, "i(ng|se)$")
```


```{r}
x <- "1888 is the longest year in Roman numerals: MDCCCLXXXVIII"
str_view(x, "CC?")
str_view(x, "CC+")
str_view(x, 'C[LX]+')
```

```{r}
str_view(x, "C{2}")
str_view(x, "C{2,}")
str_view(x, "C{2,}")

str_view(x, 'C{2,3}?')
str_view(x, 'C[LX]+?')
```

## Exercise 14.3.4.1
#### ? <- {0,1}, + <- {1,}, * <- {0,}

```{r}
str_view(fruit, "(..)\\1", match = TRUE)
```

## Exercise 14.3.5.1
#### (.)\1\1 will find consecutive triplets of a character, (.)(.)\\2\\1 will find a pair of characters that are forward then reversed, (..)/1 will find a pair of characters in an abab pattern,  (.).\\1.\\1 will find a characters in an abaca pattern, and (.)(.)(.).*\\3\\2\\1 will find 3 characters followed by any number of random characters and then the original 3 characters reversed

```{r}
x <- c("apple", "banana", "pear")
str_detect(x, "e")
```

```{r}
sum(str_detect(words, "^t"))
mean(str_detect(words, "[aeiou]$"))
```

```{r}
no_vowels_1 <- !str_detect(words, "[aeiou]")
no_vowels_2 <- str_detect(words, "^[^aeiou]+$")
identical(no_vowels_1, no_vowels_2)
```

```{r}
words[str_detect(words, "x$")]
str_subset(words, "x$")

df <- tibble(
  word = words, 
  i = seq_along(word)
)
df %>% 
  filter(str_detect(word, "x$"))
```

```{r}
x <- c("apple", "banana", "pear")
str_count(x, "a")
mean(str_count(words, "[aeiou]"))

df %>% 
  mutate(
    vowels = str_count(word, "[aeiou]"),
    consonants = str_count(word, "[^aeiou]")
  )
```

```{r}
str_count("abababa", "aba")
str_view_all("abababa", "aba")
```

## Exercsise 14.4.1.1
```{r}
str_detect(x, "^x|x$")
str_detect(x, "^[aeiou].*[^aeiou]$")
```

```{r}
# There is not a simple regular expression to match words that that contain at least one of each vowel. The regular expression would need to consider all possible orders in which the vowels could occur.
pattern <-
  cross(rerun(5, c("a", "e", "i", "o", "u")),
    .filter = function(...) {
      x <- as.character(unlist(list(...)))
      length(x) != length(unique(x))
    }
  ) %>%
  map_chr(~str_c(unlist(.x), collapse = ".*")) %>%
  str_c(collapse = "|")

str_subset("aseiouds", pattern)
#> [1] "aseiouds"


str_subset(words, pattern)
#> character(0)

words[str_detect(words, "a") &
  str_detect(words, "e") &
  str_detect(words, "i") &
  str_detect(words, "o") &
  str_detect(words, "u")]
```

```{r}
length(sentences)
head(sentences)
```

```{r}
colours <- c("red", "orange", "yellow", "green", "blue", "purple")
colour_match <- str_c(colours, collapse = "|")
colour_match
```

```{r}
has_colour <- str_subset(sentences, colour_match)
matches <- str_extract(has_colour, colour_match)
head(matches)
```

```{r}
has_colour
```

```{r}
more <- sentences[str_count(sentences, colour_match) > 1]
str_view_all(more, colour_match)

str_extract_all(more, colour_match)

str_extract_all(more, colour_match, simplify = TRUE)
```

```{r}
x <- c("a", "a b", "a b c")
str_extract_all(x, "[a-z]", simplify = TRUE)
```

## Exercise 14.4.2.1
#### colour_match <- str_c("\\b(", str_c(colours, collapse = "|"), ")\\b")

```{r}
noun <- "(a|the) ([^ ]+)"

has_noun <- sentences %>%
  str_subset(noun) %>%
  head(10)
has_noun %>% 
  str_extract(noun)
```

```{r}
has_noun %>% 
  str_match(noun)
```

```{r}
tibble(sentence = sentences) %>% 
  tidyr::extract(
    sentence, c("article", "noun"), "(a|the) ([^ ]+)", 
    remove = FALSE
  )
```

## Exercise 14.4.3.1
```{r}
numword <- "\\b(one|two|three|four|five|six|seven|eight|nine|ten) +(\\w+)"
sentences[str_detect(sentences, numword)] %>%
  str_extract(numword)
```

```{r}
x <- c("apple", "pear", "banana")
str_replace(x, "[aeiou]", "-")
str_replace_all(x, "[aeiou]", "-")
```

```{r}
x <- c("1 house", "2 cars", "3 people")
str_replace_all(x, c("1" = "one", "2" = "two", "3" = "three"))

sentences %>% 
  str_replace("([^ ]+) ([^ ]+) ([^ ]+)", "\\1 \\3 \\2") %>% 
  head(5)
```

## Exercise 14.4.4.1
```{r}
str_replace_all("past/present/future", "/", "\\\\")
```

```{r}
sentences %>%
  head(5) %>% 
  str_split(" ")
```

```{r}
"a|b|c|d" %>% 
  str_split("\\|") %>% 
  .[[1]]
```

```{r}
sentences %>%
  head(5) %>% 
  str_split(" ", simplify = TRUE)
```

```{r}
fields <- c("Name: Hadley", "Country: NZ", "Age: 35")
fields %>% str_split(": ", n = 2, simplify = TRUE)
```

```{r}
x <- "This is a sentence.  This is another sentence."
str_view_all(x, boundary("word"))
```

```{r}
str_split(x, " ")[[1]]
str_split(x, boundary("word"))[[1]]
```

## Exercise 14.4.5.1
```{r}
x <- c("apples, pears, and bananas")
str_split(x, ", +(and +)?")[[1]]
```

